---
title: "Post-Shock Forecasting with Donor Balancing Weights in R"
author: "Qiyang Wang"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
    toc: true
fontsize: 11pt
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.width = 6.5,
  fig.height = 4
)

library(tidyverse)
library(lubridate)
if (requireNamespace("devtools", quietly = TRUE)) {
  devtools::load_all("..")  
} else {
  library(postshock)
}

```

# Abstract

We develop a modular R framework for donor-based post-shock forecasting of time series that jointly addresses structural changes in both conditional mean and conditional volatility. The framework is organized as a layered forecasting architecture that integrates shock encoding, donor weighting, shock-effect estimation, and target forecasting within a unified pipeline. It is applicable in settings where a target series and related donor series are observed on a common time grid; we illustrate the approach using financial data.

The package provides four principal components: a donor balancing weights procedure (`dbw`) for constructing convex combinations of donor series on a pre-shock window; a synthetic prediction module (`SynthPrediction`) for post-shock mean forecasting via ARIMA/ARIMAX models; an automatic GARCH-X model selection routine (`auto_garchx`) for volatility modeling; and a volatility-oriented synthetic forecasting procedure (`SynthVolForecast`).

The mean-forecasting module is extended in two important directions. First, a flexible shock-control mechanism allows users to specify multiple confounding shocks with configurable shapes (point, window, or step effects), which are incorporated as structured exogenous regressors in ARIMAX modeling of the target. Second, a hierarchical multi-pool aggregation scheme enables donors to be partitioned into heterogeneous groups, with shock effects aggregated within pools and subsequently combined across pools. These extensions improve robustness, interpretability, and flexibility in practical applications.

This technical report documents the modeling framework, software design, and empirical pipeline. All results are fully reproducible through the accompanying RMarkdown file and the `postshock` package.

# Introduction

Time series observed in economics, finance, environmental science, and related domains frequently experience structural shocks. Examples include policy announcements that alter regulatory regimes, supply disruptions affecting commodity markets, financial crises, or abrupt shifts in demand triggered by major events. When such shocks occur, models estimated solely on pre-shock data—such as standard ARIMA or GARCH specifications—may fail to provide reliable forecasts in the post-shock period.

In many empirical settings, however, the analyst has access not only to a single target series but also to related auxiliary series that may serve as donors. These donor series may have experienced similar shocks in the past or may share structural drivers with the target. Donor-based approaches exploit this information by constructing weighted combinations of donor series that approximate the pre-shock behavior of the target. The donor pool is used to estimate the magnitude of post-shock adjustments, which are transferred to the target forecast via donor-balancing weights.

Structural shocks frequently affect not only the conditional mean but also the conditional variance dynamics of a time series. Sudden regime changes may alter volatility persistence, clustering behavior, or the impact of exogenous drivers. Accordingly, the proposed framework incorporates a parallel volatility module based on structured GARCH-X modeling. The `auto_garchx` procedure provides systematic model selection for the variance equation, while `SynthVolForecast` integrates donor-weighted post-shock adjustments into volatility forecasting. Together, these components establish a unified post-shock workflow for both first- and second-moment dynamics.

Conventional forecasting approaches typically treat the target series in isolation or incorporate donors as simple exogenous regressors within ARIMAX-type models. Such approaches do not explicitly enforce pre-shock balance between the target and donors and may therefore fail to extract the most informative donor combinations. Furthermore, many empirical implementations remain problem-specific and embedded in ad hoc scripts, limiting reproducibility and extensibility.

The `postshock` package addresses these limitations by providing a structured and reusable R implementation of donor-based post-shock forecasting. Rather than presenting a collection of isolated functions, the framework is organized as a layered forecasting architecture integrating shock encoding, donor weighting, shock-effect estimation, hierarchical aggregation, and target forecasting within a unified pipeline.

## Layered forecasting architecture

The framework consists of five components. These components operate sequentially as a structured pipeline, ensuring that shock encoding, donor balancing, effect estimation, aggregation, and forecasting are performed within a unified and reproducible workflow.

**Volatility module (parallel pipeline).** In addition to the five-layer mean-forecasting architecture, the framework implements a complementary volatility forecasting module based on structured GARCH-X modeling. This module extends donor-based post-shock adjustment to conditional variance dynamics. Structural shocks may enter the variance equation through exogenous regressors, enabling explicit modeling of regime shifts in volatility persistence and clustering behavior. The `auto_garchx` procedure provides systematic model selection for the variance equation, while `SynthVolForecast` integrates donor-weighted shock adjustments into volatility forecasting.

### Shock encoding and control

User-specified shock events—including both the primary shock of interest and additional confounding shocks—are translated into structured exogenous regressors for ARIMA/ARIMAX models. The primary shock defines the post-shock forecasting horizon, while control shocks are incorporated into the target baseline model to account for unrelated structural disturbances. Control shocks may be specified with flexible shapes (point, window, or step effects), allowing systematic treatment of temporary or persistent confounding events.

### Donor weighting

The `dbw()` procedure constructs convex combinations of donor series over a pre-shock window, optionally incorporating feature scaling and regularization. This ensures that the synthetic donor combination closely matches the pre-shock behavior of the target.

### Shock-effect estimation

For each donor, post-shock effects are estimated using ARIMA/ARIMAX models augmented with post-shock indicators.

### Hierarchical aggregation (single-pool or multi-pool)

Donor shock effects may be aggregated either within a single donor pool or through a hierarchical multi-pool structure. In the multi-pool setting, donors are partitioned into economically interpretable groups (for example, supply-side versus demand-side shocks). Shock effects are first aggregated within pools and subsequently combined across pools. This structure accommodates heterogeneous shock mechanisms, enhances interpretability, and mitigates cross-group contamination.

### Target forecasting

The aggregated shock adjustment is incorporated into the target forecast, which is estimated using ARIMA/ARIMAX models and may also include control shocks.

This modular design separates the donor-balancing machinery from the time-series modeling layer. The current implementation supports ARIMA/ARIMAX models for the mean equation and GARCH-X models for the volatility equation, while remaining extensible to alternative specifications.

Our methodology is inspired by donor-pool ideas such as those of Lin and Eck (2021), who aggregate shocks from related series to construct shock estimators. The present framework generalizes this idea in two directions. First, it introduces a structured shock-control mechanism for handling multiple confounding events within a unified modeling interface. Second, it extends single-pool aggregation to a hierarchical multi-pool design, enabling structured decomposition of heterogeneous shock transmission mechanisms. Together, these extensions transform a problem-specific implementation into a reusable and extensible forecasting architecture.

The empirical analysis builds on Experiment 1 in Lin and Eck (2021), focusing on post-shock forecasting for ConocoPhillips stock using the same underlying data. While Lin and Eck emphasize an AR(1)-based, case-specific implementation, our framework provides a general donor-based architecture supporting both mean and volatility dynamics. Using the ConocoPhillips data as a benchmark, we demonstrate improved post-shock forecast performance and illustrate broader applicability.

## Roadmap

The remainder of the report is organized as follows. Section 3 introduces the notation and describes the methodological components of the framework. Section 4 presents the data and empirical setup. Section 5 reports simulation results for both the mean and volatility equations. Section 6 provides an empirical application to ConocoPhillips and discusses forecasting performance under large shocks.

#  Methodology and Implementation

## Problem setup and notation

The primary objective of the `postshock` package is to address the failure of traditional forecasting models in the presence of **substantial structural shocks**. Under such "big shocks," baseline models (like ARIMA or GARCH) estimated on pre-shock data typically suffer from severe bias as the underlying data-generating process undergoes a radical shift. Our framework leverages a **donor-based counterfactual approach** to adjust these forecasts by borrowing "shock signatures" from historical donor episodes.

### Regime Boundaries and Timing

We consider a target time series $Y_{0,t}$ and $J$ donor series $Y_{j,t}$. We model the shock not as a point-event, but as a **regime shift**—a transition from a stable baseline to a post-shock state. 

To facilitate the donor-based adjustment, all series are aligned relative to their respective shock inception points. For each series $j \in \{0, \dots, J\}$, we define **$T_0$** as the **terminal boundary of the pre-shock regime**.

* **Pre-shock Regime**: The period $t \in \{1, \dots, T_0\}$ where the series follows its undisturbed dynamics.
* **Post-shock Regime**: The period $t > T_0$ where the "big shock" effect begins to materialize.

The index $T_0$ represents the **last "clean" observation** for the series in its truncated or aligned form. Thus, $T_0+1$ is the **inception of the shock effect**, regardless of whether the physical catalyst occurred exactly at a time index or in the interval between observations (e.g., overnight market news).



### The Post-Shock Forecasting Objective

The framework is designed to correct the target's trajectory $Y_{0, T_0+1}, \dots, Y_{0, T_0+k}$ following a major disruption. We decompose the final forecast into a "no-shock" baseline and a donor-informed synthetic adjustment $\hat{\omega}_h$:

\[
\hat{Y}_{0, T_0+h} = \underbrace{\hat{Y}_{0, T_0+h}^{\text{baseline}}}_{\text{Standard ARIMA/GARCH}} + \underbrace{\hat{\omega}_h}_{\text{Synthetic Shock Adjustment}}, \quad h = 1, \dots, k
\]

This decomposition explicitly targets the bias introduced by big shocks, ensuring that $\hat{\omega}_h$ captures the magnitude of the regime shift that standard models would otherwise ignore.

### Software Mapping

In the `postshock` package, the theoretical boundaries and regime definitions are operationalized through specific user-supplied arguments. To ensure the framework correctly captures the magnitude of the shock, the data must be aligned as follows:

* **Regime Boundaries ($T_0$):** Specified via the `shock_time_vec` argument. Each element $j$ in this vector must be the **integer index of the last clean observation** for that specific series $Y_j$.
    * *Example:* `shock_time_vec <- c(500, 450, 600)`
* **Shock Observation Depth ($L_j$):** Specified via `shock_length_vec`. This defines the number of observations *after* $T_0$ (i.e., from $T_0+1$ to $T_0+L_j$) used to extract the "shock signature" from each donor.
    * *Example:* `shock_length_vec <- c(10, 10, 10)`
* **Data Structures:** The series and their respective pre-shock characteristics are passed as lists (`Y_series_list` and `covariates_series_list`). The order of elements in these lists must strictly match the order in `shock_time_vec`.

## Donor balancing weights (`dbw`)

The first component of the framework is a donor balancing weights procedure, implemented in the function `dbw()`. The goal is to construct a weight vector
\[
\omega = (\omega_1,\dots,\omega_J)^\top
\]
on the donor series such that a weighted combination of donors closely matches the target on a pre-shock window. Intuitively, donors that look more similar to the target before the shock should receive larger weights, while dissimilar donors should receive smaller (or zero) weights.

For exposition, suppose that each series is represented by a feature vector \(z_i \in \mathbb{R}^K\) summarizing its pre-shock history, where \(i=0\) denotes the target and \(i=1,\dots,J\) denote the donors. These features can include raw covariates at the last pre-shock time, multiple lookback values, and transformed auxiliary information, as described below. Let
\[
z_0 \in \mathbb{R}^K \quad\text{and}\quad
Z_0 = \begin{pmatrix} z_1^\top \\ \vdots \\ z_J^\top \end{pmatrix} \in \mathbb{R}^{J \times K}
\]
collect the target feature vector and the donor feature matrix. A basic formulation of the donor balancing problem is then
\[
\min_{\omega} \ \bigl\| z_0 - Z_0^\top \omega \bigr\|_p + \lambda \cdot \text{pen}(\omega)
\quad\text{subject to}\quad
\sum_{j=1}^J \omega_j = 1,\qquad
L \le \omega_j \le U \ \text{for all } j,
\]
where \(\|\cdot\|_p\) is either an \(\ell_1\) or \(\ell_2\) norm, \(\lambda \ge 0\) is a regularization parameter, \(\text{pen}(\omega)\) is an \(\ell_1\) (LASSO-type) or \(\ell_2\) (ridge-type) penalty on the weights, and \(L,U\) are lower and upper bounds. The simplex constraint \(\sum_j \omega_j = 1\) together with nonnegative bounds ensures that \(\omega\) can be interpreted as convex combination weights on the donors.

For clarity, we summarize the main notation used in this section. The integer \(J\) denotes the number of donor series, and \(K\) is the dimension of the feature vectors used for balancing. For each series \(i\), the vector \(z_i \in \mathbb{R}^K\) collects its pre-shock features, with \(z_0\) corresponding to the target and \(z_1,\dots,z_J\) to the donors. The matrix \(Z_0 \in \mathbb{R}^{J\times K}\) stacks the donor features row-wise, so that \(Z_0^\top \omega\) is the weighted donor feature vector under weights \(\omega = (\omega_1,\dots,\omega_J)^\top \in \mathbb{R}^J\). The parameter \(p \in \{1,2\}\) determines whether an \(\ell_1\) or \(\ell_2\) norm is used in the matching loss, and \(\lambda \ge 0\) controls the strength of the penalty \(\text{pen}(\omega)\), which can be either \(\ell_1\)-type (LASSO) or \(\ell_2\)-type (ridge) depending on the argument `penalty_normchoice`. The constants \(L\) and \(U\) are lower and upper bounds on each weight, typically \(L=0\) and \(U=1\), while the equality constraint \(\sum_{j=1}^J \omega_j = 1\) (corresponding to `sum_to_1 = TRUE`) enforces that \(\omega\) defines a convex combination of the donor series.

In the `postshock` implementation, the input `X` is a list of data frames or matrices. The first element `X[[1L]]` contains the target series, and the remaining elements `X[[2L]]`, …, `X[[J+1L]]` contain the donors. Rows correspond to time and columns to features. The integer vector `dbw_indices` selects which feature columns are used in the matching objective. The vector `shock_time_vec` has the same length as `X` and records, for each series, the last pre-shock row; each series is truncated to rows `1:shock_time_vec[i]` before any further processing.

Several options control how the feature vectors \(z_i\) are constructed:

- The optional list `Y` can contain auxiliary series for each element of `X`, for example returns or transformed variables.  
- The argument `Y_lookback_indices` specifies which backwards-looking rows of `Y[[i]]` are to be used (for example, `c(1, 2, 5)` corresponds to the last, second last, and fifth last pre-shock rows), and the function `inputted_transformation` is applied to each `Y[[i]]` before these lookback values are extracted.  
- Similarly, `X_lookback_indices` can be used to extract multiple lookback rows from the truncated `X[[i]]`; if `X_lookback_indices` is `NULL`, only the final pre-shock row is used.  

The selected rows are vectorized and concatenated to form a single feature vector for each series. Constant columns are removed automatically, and optional centering and scaling are applied via the logical arguments `center` and `scale`. If `princ_comp_count` is not `NULL`, a principal component analysis is performed and only the specified number of leading components are retained, which can help mitigate collinearity in high-dimensional settings.

Distance and regularization choices are controlled by the arguments `normchoice`, `penalty_normchoice`, and `penalty_lambda`. The argument `normchoice` is either `"l1"` or `"l2"`, corresponding to \(\ell_1\) or \(\ell_2\) distance in the matching loss. The argument `penalty_normchoice` selects an \(\ell_1\) (`"l1"`) or \(\ell_2\) (`"l2"`) penalty on the weights, and `penalty_lambda` is constrained to be nonnegative and specifies the penalty strength. When `sum_to_1 = TRUE` and the bounds `bounded_below_by` and `bounded_above_by` enforce nonnegative weights, the \(\ell_1\) norm of \(\omega\) is (up to numerical tolerance) fixed at one; in this regime an \(\ell_1\) penalty only adds a constant to the objective and does not change the minimizer, so an \(\ell_2\) penalty is typically more effective under simplex constraints.

Formally, the optimization problem is solved using the `solnp` routine from the `Rsolnp` package, subject to the box constraints `bounded_below_by` and `bounded_above_by` and the optional equality constraint `sum_to_1`. The function returns a list with three main components: `opt_params`, the estimated donor weight vector \(\hat{\omega}\); `loss`, the final matching loss; and `convergence`, a flag indicating whether the numerical optimizer reports successful convergence. These weights are then used inside `SynthPrediction()` and `SynthVolForecast()` to combine donor-specific forecasts for the target series.

In the empirical work of this report we adopt a convex-combination specification with $\ell_2$-regularized weights. Concretely, all examples in Sections 3–4 use the following default options:

- `sum_to_1 = TRUE`
- `bounded_below_by = 0`
- `bounded_above_by = 1`
- `normchoice = "l2"`
- `penalty_normchoice = "l2"`
- `penalty_lambda = 1e-2`

Under this configuration the weights can be interpreted as nonnegative donor shares that sum to one and therefore define a convex combination, while the $\ell_2$ penalty stabilizes the solution when donors are highly correlated. This specification corresponds to a constrained ridge-type matching problem on the simplex.

The following example illustrates the computation of donor weights using three pre-shock features.

```{r dbw-example, echo=TRUE}
set.seed(1)

T  <- 50
K  <- 3

# Construct a target and two donors with K=3 features
target <- data.frame(
  x1 = rnorm(T),
  x2 = rnorm(T,  0.2),
  x3 = rnorm(T, -0.1)
)
donor1 <- data.frame(
  x1 = rnorm(T,  0.1),
  x2 = rnorm(T, -0.1),
  x3 = rnorm(T,  0.3)
)
donor2 <- data.frame(
  x1 = rnorm(T, -0.2),
  x2 = rnorm(T,  0.4),
  x3 = rnorm(T,  0.0)
)

X_list <- list(target, donor1, donor2)
shock  <- c(40, 40, 40)   # last pre-shock row for each series

dbw_out <- dbw(
  X                 = X_list,
  dbw_indices       = 1:K,
  shock_time_vec    = shock,
  center            = TRUE,
  scale             = TRUE,
  sum_to_1          = TRUE,
  bounded_below_by  = 0,
  bounded_above_by  = 1,
  normchoice        = "l2",
  penalty_normchoice = "l2",
  penalty_lambda    = 1e-2
)

cat("Estimated donor weights:\n")
print(round(dbw_out$opt_params, 3))

cat("\nFinal matching loss:\n")
print(dbw_out$loss)

cat("\nConvergence flag:\n")
print(dbw_out$convergence)

```


## Synthetic mean forecasting (`SynthPrediction`)

The second component of the framework is a synthetic mean–forecasting
procedure, implemented in the function `SynthPrediction()`.  The aim is to
produce \(k\)-step-ahead forecasts for a target series by combining
information from a pool of donor series that have experienced structural
shocks in the past.  The procedure operates in four layers:
(i) estimation of donor-specific shock effects via (S)ARIMA models with a
post-shock indicator; (ii) construction of donor weights (either equal or
DBW-based); (iii) fitting an ARIMA model to the pre-shock portion of the
target; and (iv) adjusting the target forecast by the weighted donor shock
effect.

For notation, let \(Y_{i,t}\) denote the value of series \(i=0,1,\dots,J\) at
time \(t\), where \(i=0\) is the target and \(i=1,\dots,J\) are donors.
For each series we observe a shock start time \(T_i\) and a post-shock window
length \(L_i\).  In the implementation these are supplied via the vectors
`shock_time_vec` and `shock_length_vec`, and are first converted to integer
indices that match the time index of `Y_series_list`.

### Donor-level (S)ARIMA with post-shock indicators

For each donor \(i=1,\dots,J\), we model the series as a baseline
time-series component plus a structural shock effect. Specifically, we
consider the decomposition
\[
Y_{i,t}
=
\mu_{i,t}
+
\gamma_i D_{i,t}
+
\varepsilon_{i,t},
\]
where \( \mu_{i,t} \) follows an ARIMA or seasonal ARIMA process, \(D_{i,t}\)
is a post-shock indicator defined by
\[
D_{i,t} =
\begin{cases}
0, & t \le T_i,\\
1, & T_i < t \le T_i + L_i,
\end{cases}
\]
and \(\varepsilon_{i,t}\) denotes the innovation term. The parameter \(\gamma_i\) captures the average level shift induced by the shock over the specified window.

In the implementation, `SynthPrediction()` estimates this model using
`forecast::auto.arima()` (or a user-specified `arima_order`), with a design
matrix whose columns consist of the post-shock indicator and any selected
covariates. The function `decide_seasonal()` determines whether a seasonal
component should be included based on the detected or user-specified period.

If the argument `covariate_indices` is non-`NULL`, the donor design matrix
contains both the post-shock indicator and the selected columns of
`covariates_series_list[[i]]` as contemporaneous regressors.  If
`covariate_indices` is `NULL`, the only regressor is the post-shock
indicator.  After fitting the model, the donor shock effect
\(\widehat{\gamma}_i\) is extracted as the coefficient associated with the post-shock indicator regressor
(i.e., the post-shock indicator) using `lmtest::coeftest()`.  Collecting these
into a vector
\[
\widehat{\boldsymbol{\gamma}} = (\widehat{\gamma}_1,\dots,\widehat{\gamma}_J)^\top,
\]
we obtain donor-level estimates of how each past shock affected its
corresponding series over the specified window.

### Donor weighting

In the second layer, `SynthPrediction()` constructs donor weights
\(\boldsymbol{w} = (w_1,\dots,w_J)^\top\).  If `use_dbw = FALSE`, equal
weights \(w_j = 1/J\) are used.  If `use_dbw = TRUE`, the function calls
`dbw()` to compute data-driven weights based on pre-shock covariates.

For this purpose, the object `X_for_dbw` is formed by taking
`covariates_series_list` (if available) or falling back to `Y_series_list`.
Each element is converted to a numeric matrix.  If `dbw_indices` is `NULL`,
informative columns are selected automatically by examining cross-series
variance at the last pre-shock row and discarding nearly constant columns.
The resulting indices, together with the integer shock times, are passed to
`dbw()` along with options such as `dbw_scale`, `dbw_center`,
`penalty_lambda`, and `penalty_normchoice`.  When `dbw()` succeeds, the
optimal weights \(\widehat{\boldsymbol{w}}\) are taken from
`dbw_output$opt_params`; otherwise the procedure falls back to equal weights.

The combined donor shock effect used for adjustment is then
\[
\widehat{\theta} = \sum_{j=1}^J \widehat{w}_j \widehat{\gamma}_j,
\]
which aggregates individual donor effects according to their DBW weights.

### Target (S)ARIMA and shock adjustment

In the third layer, we fit an ARIMA model to the target series using only
pre-shock data.  Let \(T_0\) denote the last pre-shock time for the target.
`SynthPrediction()` restricts the target series to observations
\(t = 1,\dots,T_0\) and fits an ARIMA or seasonal ARIMA model in the same
manner as for the donors, using `auto.arima()` or a user-specified
`arima_order`.  If `covariate_indices` is non-`NULL`, the selected columns of
`covariates_series_list[[1]]` are lagged by one period (via `lag.xts`) and
included as `xreg` for model fitting.  For forecasting, the last pre-shock
covariate row is replicated \(k\) times to form the `newxreg` matrix, so that
the \(k\)-step-ahead forecasts correspond to holding the covariates fixed at
their last observed values.

Let \(\widehat{Y}^{\text{raw}}_{0,T_0+h}\) denote the resulting raw forecast
for the target at horizon \(h = 1,\dots,k\).  The adjusted “DBW version”
forecast is defined by
\[
\widehat{Y}^{\text{adj}}_{0,T_0+h}
  = \widehat{Y}^{\text{raw}}_{0,T_0+h} + \widehat{\theta},
\]
which adds the weighted donor shock effect \(\widehat{\theta}\) to the raw
ARIMA forecast. This adjustment relies on the identifying assumption that the weighted donor shock effect provides a consistent proxy for the counterfactual shock effect on the target under comparable structural conditions. For comparison, the function also computes an “arithmetic
mean” version that uses the simple average of donor effects,
\[
\widehat{Y}^{\text{arith}}_{0,T_0+h}
  = \widehat{Y}^{\text{raw}}_{0,T_0+h}
    + \frac{1}{J} \sum_{j=1}^J \widehat{\gamma}_j.
\]

The outputs of `SynthPrediction()` are collected in a list with three main
components.  The element `linear_combinations` contains the donor weight
vector \(\widehat{\boldsymbol{w}}\); `predictions` contains three forecast
vectors labelled `unadjusted`, `adjusted`, and `arithmetic_mean`; and `meta`
stores additional information such as the donor-specific \(\widehat{\gamma}_j\),
the combined effect \(\widehat{\theta}\), the ARIMA orders, and the information
criterion used.  These objects are used in Section 4 to construct the
empirical results.

#### Illustrative simulation example

To illustrate how `SynthPrediction()` behaves in a simple setting, we simulate one
target series and two donor series observed on a daily grid with \(T = 200\).
The target \(Y_0\) is a random walk around level 100. Donor 1 is a very close
copy of the target (small extra noise), while donor 2 is much noisier. As
covariates we construct a second random walk (“base signal”) and create two
highly informative covariates \(X_0, X_1\) plus one largely uninformative
covariate \(X_2\). We treat time index \(T_0 = 150\) as the shock time for all
series and estimate a one–step–ahead forecast (\(k=1\)).

```{r synthprediction-example, echo=TRUE}
library(xts)
set.seed(123)

## 1) Target and donors ---------------------------------
T     <- 200
dates <- seq.Date(as.Date("2021-01-01"), by = "day", length.out = T)

# target: random walk around level 100
y0 <- cumsum(rnorm(T, mean = 0, sd = 1)) + 100
Y0 <- xts(y0, order.by = dates)

# donor 1: very similar to target (small extra noise)
y1 <- y0 + rnorm(T, mean = 0, sd = 0.1)
Y1 <- xts(y1, order.by = dates)

# donor 2: noisier copy of target
y2 <- y0 + rnorm(T, mean = 0, sd = 2)
Y2 <- xts(y2, order.by = dates)

Y_list <- list(Y0, Y1, Y2)

## 2) Covariates ---------------------------------------
base_signal <- cumsum(rnorm(T, mean = 0, sd = 1))   # common latent factor

X0 <- xts(base_signal + rnorm(T, sd = 0.1), order.by = dates)
X1 <- xts(base_signal + rnorm(T, sd = 0.1), order.by = dates)
X2 <- xts(cumsum(rnorm(T, sd = 2)),        order.by = dates)  # less informative

X_list <- list(X0, X1, X2)

## 3) Shock specification ------------------------------
shock_time_vec   <- c(150, 150, 150)  # shock happens at time 150
shock_length_vec <- c(1L,  1L,  1L)   # one-step post-shock window

## 4) Run SynthPrediction ------------------------------
res <- SynthPrediction(
  Y_series_list          = Y_list,
  covariates_series_list = X_list,
  shock_time_vec         = shock_time_vec,
  shock_length_vec       = shock_length_vec,
  k                      = 1,
  covariate_indices      = 1,
  seasonal               = FALSE,
  plots                  = FALSE
)

res$linear_combinations      # DBW donor weights
res$predictions              # raw / adjusted forecasts

# True value of Y0 at T0+1 (time 151)
Y_list[[1]][150:151]
truth <- as.numeric(Y_list[[1]][151])

c(
  truth      = truth,
  raw        = res$predictions$unadjusted[1],
  dbw_adj    = res$predictions$adjusted[1],
  arith_mean = res$predictions$arithmetic_mean[1]
)

```

## Structured donor pools (MultiPool extension)

In many empirical applications, donor series may reflect **heterogeneous shock
channels** rather than a single homogeneous source of post-shock variation. For
instance, structural breaks may be driven by supply-side disruptions,
demand-side shifts, or policy interventions operating through distinct
mechanisms. Treating all donors as a single undifferentiated pool can mask this
structure and reduce interpretability.

To accommodate heterogeneous channels, we extend the synthetic mean forecasting
framework to a **multi-pool** setting. This extension is implemented via
automatic dispatch within `SynthPrediction()` when the argument `pools` is
provided. Conceptually, the multi-pool workflow (i) constructs a single common
baseline counterfactual forecast using the full donor set, and (ii) extracts
pool-level shock proxies from restricted donor subsets, which are then combined
according to a user-specified aggregation rule.

### Pool structure and notation

Let \(Y_{i,t}\), \(i = 0,1,\dots,J\), denote the target series (\(i=0\)) and
donor series (\(i=1,\dots,J\)) observed over time \(t\). Donors are partitioned
into \(G\) **potentially overlapping pools**
\[
\mathcal{J}_1, \dots, \mathcal{J}_G,
\]
supplied as a named list
\[
\texttt{pools} = \{\mathcal{J}_g\}_{g=1}^G,
\]
where each element contains donor series names that match
`names(Y_series_list)`. The first element of `Y_series_list` is always treated
as the target.

> **Practical requirement.** Since pools refer to donors by name, `Y_series_list`
> (and, if provided, `covariates_series_list`) must be named with consistent
> ordering.


### Step 1: Common baseline forecast (unique counterfactual)

The procedure first computes a **single baseline forecast** by calling
`SynthPrediction()` on the full donor set (without pool structure). This defines
the unique counterfactual forecasting path used throughout the multi-pool
procedure and produces a raw \(k\)-step-ahead forecast
\[
\widehat{Y}^{\mathrm{raw}}_{0,T_0+h}, \quad h=1,\dots,k,
\]
stored as `predictions$unadjusted`.

Whether donor balancing weights (DBW) are used in this baseline run is
controlled by `base_use_dbw`.

> **Role of Step 1.** Step 1 defines the only baseline counterfactual forecast.
> All multi-pool variants differ only in how the shock adjustment term is
> constructed, not in how the raw counterfactual path is generated.


### Step 2: Pool-specific shock proxies (channel extraction)

For each pool \(g\), the algorithm:

1. Subsets the series list to include the target and the donors in
   \(\mathcal{J}_g\).

2. Runs `SynthPrediction()` on this restricted subset, optionally using DBW
   within the pool (controlled by `pool_use_dbw`).

3. Extracts the pool-level combined donor shock quantity
   \[
   \widehat{\theta}_g \equiv \widehat{\omega}_g,
   \]
   obtained from the subset output’s `meta$combined_omega`.

Each \(\widehat{\theta}_g\) is interpreted as a **pool-specific shock proxy**
capturing the contribution of the structural channel represented by pool \(g\)
under comparable pre-shock conditions. Importantly, the pool-specific runs are
**not used as alternative forecasts**; they serve only as devices to extract
pool-level shock proxies under donor restrictions.

Collecting across pools yields
\[
\widehat{\boldsymbol{\theta}}
=
(\widehat{\theta}_1,\dots,\widehat{\theta}_G)^\top.
\]

> **DBW at baseline vs within pools.** DBW at baseline enforces global pre-shock
> balance using the full donor set. DBW within pools enforces balance conditional
> on the pool restriction. These serve distinct roles and should not be
> interpreted as “double balancing” the same objective.


### Step 3: Cross-pool aggregation (constructing the adjustment)

The pool-level shock proxies \(\widehat{\boldsymbol{\theta}}\) are aggregated into a single scalar adjustment term \(\widehat{\theta}\) using the pool_agg rule.

- **Sum aggregation**
  \[
  \widehat{\theta}
  =
  \sum_{g=1}^G \widehat{\theta}_g.
  \]

- **Weighted aggregation**
  Given user-specified weights \(\pi_g\),
  \[
  \widehat{\theta}
  =
  \sum_{g=1}^G \pi_g \widehat{\theta}_g.
  \]
  The weighted case requires a named numeric vector aligned with pool names.
  
  

> **Modeling choice.** Sum aggregation corresponds to an additive structural
> decomposition of the target shock effect across channels. Weighted aggregation
> imposes a user-specified contribution profile. Neither aggregation rule is
> implied by the data; both encode modeling/identification assumptions.


### Step 4: Multi-pool adjusted forecast

The final multi-pool forecast is defined as
\[
\widehat{Y}^{\mathrm{adj,mp}}_{0,T_0+h}
=
\widehat{Y}^{\mathrm{raw}}_{0,T_0+h}
+
\widehat{\theta}, \quad h=1,\dots,k.
\]
This adjusted series is stored as `predictions$adjusted_multipool`.

Importantly, the baseline raw forecast is unchanged; only the shock adjustment
term differs across pooling strategies.

### Output structure

The multi-pool extension preserves the original output of `SynthPrediction()`
and adds:

- `predictions$adjusted_multipool`,
- `meta$multi_pool`, which contains
  - the pool definitions,
  - pool-specific shock proxies \(\{\widehat{\theta}_g\}\),
  - aggregation rule and (optional) weights,
  - aggregated adjustment \(\widehat{\theta}\),
  - indicators of whether DBW was used at baseline or within pools.

This design enables **decomposition analysis**, allowing practitioners to
attribute portions of the final adjustment to distinct structural channels as
encoded by the donor pools.

### Identification interpretation

The multi-pool framework generalizes the single-pool identifying assumption by
allowing donor heterogeneity to be represented explicitly through pool
structure.

Within each pool \(g\), the pooled donor shock proxy \(\widehat{\theta}_g\) is
assumed to provide a valid proxy for the corresponding structural component of
the target’s counterfactual shock effect under comparable pre-shock conditions.

When sum aggregation is used, an additional **additive separability**
assumption is invoked:
\[
\theta_{\text{target}}
=
\sum_{g=1}^G \theta_g.
\]
Under this assumption, the aggregated adjustment \(\widehat{\theta}\) provides a
reduced-form estimate of the total shock adjustment constructed from the sum of
pool-level components. This hierarchical structure relaxes the homogeneous-donor
assumption of the baseline method while preserving interpretability and
computational tractability.

```{r synthprediction-multipool-example, echo=TRUE}
## MultiPool example: reuse the same simulated data above -----------------

# 0) IMPORTANT: MultiPool requires named lists (pools refer to donors by name)
names(Y_list) <- c("target", "donor_close", "donor_noisy")
names(X_list) <- c("target", "donor_close", "donor_noisy")  # keep aligned with Y_list

# 1) Define donor pools (channels)
pools <- list(
  close_copy = c("donor_close"),
  noisy_copy = c("donor_noisy")
)

# 2) Example pool weights (must align with pool names)
pool_weights <- c(
  close_copy = 0.5,
  noisy_copy = 0.5
)

# 3) Run MultiPool with weighted aggregation
res_mp <- SynthPrediction(
  Y_series_list          = Y_list,
  covariates_series_list = X_list,
  shock_time_vec         = shock_time_vec,
  shock_length_vec       = shock_length_vec,
  k                      = 1,
  covariate_indices      = 1,
  seasonal               = FALSE,
  plots                  = FALSE,
  pools                  = pools,
  pool_agg               = "weighted",
  pool_weights           = pool_weights,
  base_use_dbw           = TRUE,
  pool_use_dbw           = TRUE
)

# Inspect pool effects + aggregated effect
res_mp$meta$multi_pool$pool_effects
res_mp$meta$multi_pool$aggregated_effect

# Compare forecasts
c(
  truth          = truth,
  raw            = res_mp$predictions$unadjusted[1],
  single_adj_dbw = res_mp$predictions$adjusted[1],
  multipool_adj  = res_mp$predictions$adjusted_multipool[1]
)
```

## Adjustment for additional confounding shocks

In empirical applications, the primary shock of interest may not be the only
event affecting the target series during the post-shock period. Additional
confounding shocks—such as subsequent product releases, policy announcements,
or macroeconomic disturbances—may occur within or shortly after the main shock
window. If left unaccounted for, these confounding shocks can bias the estimated
shock adjustment and distort counterfactual forecasts.

To address this issue, the proposed framework allows **explicit control for
additional confounding shocks** through structured shock regressors included
in the forecasting model.

### Confounding shock specification

Let \(T_0\) denote the onset of the primary shock of interest. Suppose that
additional confounding shocks occur at times
\[
T_1, T_2, \dots, T_M,
\]
with corresponding durations
\[
L_1, L_2, \dots, L_M.
\]

For each confounding shock \(m = 1,\dots,M\), we construct a deterministic shock
indicator
\[
D_{m,t} =
\mathbf{1}\{T_m \le t < T_m + L_m\},
\]
or, more generally, a user-specified shock profile (e.g., step, pulse, or
finite window effect). These indicators are collected into a matrix of
confounding shock regressors
\[
\mathbf{D}_t = (D_{1,t}, \dots, D_{M,t})^\top.
\]

The shock specification mechanism is shared with the primary shock and is
implemented via the arguments `shock_time_vec` and `shock_length_vec`, allowing
multiple shocks to be declared simultaneously.

### Forecasting model with confounding shocks

Let \(Y_{0,t}\) denote the target series. Conditional on the donor-based
counterfactual structure, the forecasting equation is augmented to include
confounding shocks as exogenous regressors:
\[
Y_{0,t}
=
\mu_t
+
\alpha \, \mathbf{1}\{t \ge T_0\}
+
\boldsymbol{\gamma}^\top \mathbf{D}_t
+
\varepsilon_t,
\]
where:
- \(\mu_t\) represents the counterfactual mean forecast generated from donors,
- \(\alpha\) captures the effect of the primary shock of interest,
- \(\boldsymbol{\gamma}\) captures the effects of confounding shocks,
- \(\varepsilon_t\) is an idiosyncratic error term.

The confounding shock coefficients \(\boldsymbol{\gamma}\) are estimated jointly
with the primary shock effect within the forecasting model, ensuring that the
estimated adjustment for the shock of interest is **orthogonalized with respect
to known confounding events**.

### Relation to additive shock decomposition

This approach is closely related to empirical strategies that decompose observed
outcomes into additive effects of multiple structural shocks. For example,
existing work in macroeconomics and energy economics studies supply- and
demand-driven shocks by modeling their effects as additive components of the
observed response.

In contrast to structural VAR approaches—where additivity parameters are
estimated within a fully parametric system—the present framework adopts a
reduced-form perspective. Confounding shocks are controlled via explicit
exogenous regressors, while donor-based counterfactuals capture the underlying
baseline dynamics. Additivity across shocks is imposed as an identifying
assumption rather than inferred from a structural model.

### Interaction with MultiPool adjustment

The confounding shock adjustment operates **orthogonally** to the MultiPool
extension described in the previous section. Specifically:

1. MultiPool decomposes the primary shock effect across heterogeneous donor
   channels.
2. Confounding shock controls isolate the primary shock effect from subsequent
   or overlapping events.

When both mechanisms are used, the final adjusted forecast takes the form
\[
\widehat{Y}_{0,T_0+h}
=
\widehat{Y}^{\mathrm{raw}}_{0,T_0+h}
+
\widehat{\theta}
+
\boldsymbol{\gamma}^\top \mathbf{D}_{T_0+h},
\]
where \(\widehat{\theta}\) is the aggregated MultiPool adjustment.

This layered structure allows practitioners to disentangle (i) baseline
counterfactual dynamics, (ii) primary shock effects decomposed across donor
channels, and (iii) additional confounding shocks, within a unified forecasting
pipeline.

### Practical considerations

- Confounding shocks should be declared only when their timing and qualitative
  interpretation are well understood.
- Over-specification of shock controls may reduce efficiency, particularly in
  short post-shock samples.
- When multiple confounding shocks overlap in time, estimated coefficients
  should be interpreted jointly rather than individually.

Overall, explicit adjustment for additional confounding shocks enhances the
credibility and interpretability of post-shock forecasts, particularly in
settings where multiple discrete events affect the target series within a
narrow time window.

```{r synthprediction-example-short, echo=TRUE, message=FALSE, warning=FALSE}
library(xts)
set.seed(123)

## 1) Target and donors ---------------------------------
T     <- 200
dates <- seq.Date(as.Date("2021-01-01"), by = "day", length.out = T)

# target: random walk around level 100
y0 <- cumsum(rnorm(T, mean = 0, sd = 1)) + 100

# donor 1: very similar to target (small extra noise)
y1 <- y0 + rnorm(T, mean = 0, sd = 0.1)

# donor 2: noisier copy of target
y2 <- y0 + rnorm(T, mean = 0, sd = 2)

Y_list <- list(
  target = xts(y0, order.by = dates),
  donor1 = xts(y1, order.by = dates),
  donor2 = xts(y2, order.by = dates)
)

## 2) Covariates ---------------------------------------
base_signal <- cumsum(rnorm(T, mean = 0, sd = 1))

X_list <- list(
  target = xts(base_signal + rnorm(T, sd = 0.1), order.by = dates),
  donor1 = xts(base_signal + rnorm(T, sd = 0.1), order.by = dates),
  donor2 = xts(cumsum(rnorm(T, sd = 2)),         order.by = dates)
)

## 3) Shock specification ------------------------------
t_main <- 150L
shock_time_vec   <- rep(t_main, length(Y_list))
shock_length_vec <- rep(1L,     length(Y_list))

## 4) Run SynthPrediction (no confounding control) -----
res <- SynthPrediction(
  Y_series_list          = Y_list,
  covariates_series_list = X_list,
  shock_time_vec         = shock_time_vec,
  shock_length_vec       = shock_length_vec,
  k                      = 1,
  covariate_indices      = 1,
  seasonal               = FALSE,
  plots                  = FALSE
)

# 1-step truth (time t_main+1)
truth <- as.numeric(Y_list$target[t_main + 1])

c(
  truth      = truth,
  raw        = as.numeric(res$predictions$unadjusted[1]),
  adjusted   = as.numeric(res$predictions$adjusted[1]),
  arith_mean = as.numeric(res$predictions$arithmetic_mean[1])
)

## 5) OPTIONAL: add one confounding shock on the target only ----
# Example: a short confounding event before the main shock
t_conf   <- 120L
len_conf <- 5L

control_shocks <- vector("list", length(Y_list))
control_shocks[[1]] <- list(list(time = t_conf, length = len_conf, shape = "window"))

res_ctl <- SynthPrediction(
  Y_series_list          = Y_list,
  covariates_series_list = X_list,
  shock_time_vec         = shock_time_vec,
  shock_length_vec       = shock_length_vec,
  k                      = 1,
  covariate_indices      = 1,
  control_shocks         = control_shocks,
  seasonal               = FALSE,
  plots                  = FALSE
)

c(
  truth        = truth,
  raw          = as.numeric(res_ctl$predictions$unadjusted[1]),
  adjusted_ctl = as.numeric(res_ctl$predictions$adjusted[1])
)
```

## Volatility model selection (`auto_garchx`)


The next component of the framework is a volatility–forecasting module based on
GARCH–type models with exogenous regressors. It is implemented in the function
`auto_garchx()`, which selects a GARCHX specification by BIC and optionally
refits the selected model using a more stable backcast for the conditional
variance.

Let \(\{y_t\}_{t=1}^n\) denote a (demeaned) return series and let \(x_t\) collect
exogenous regressors (if any). Following the parametrisation of the `garchx`
package, we consider models of the form
\[
y_t = \sigma_t \varepsilon_t, \qquad \varepsilon_t \sim \text{i.i.d. }(0,1),
\]
with conditional variance
\[
\sigma_t^2
  = \omega
  + \sum_{i=1}^q \alpha_i y_{t-i}^2
  + \sum_{j=1}^p \beta_j \sigma_{t-j}^2
  + \sum_{\ell=1}^q \gamma_\ell y_{t-\ell}^2 \mathbf 1\{y_{t-\ell}<0\}
  + \delta^\top x_t .
\]
Here \(q\) is the ARCH order, \(p\) is the GARCH order, and the coefficients
\(\gamma_\ell\) capture GJR–type asymmetry. In the `garchx` implementation
these orders are supplied as an integer vector \(\texttt{order} = (q,p,o)\),
where \(o \in \{0,1\}\) indicates whether the asymmetric GJR term is included
(\(o = 1\)) or not (\(o = 0\)).

The main arguments of `auto_garchx()` are:

- `y`: numeric vector of returns or residuals (no `NA`/`Inf`/`NaN`);
- `xreg`: optional matrix of exogenous regressors aligned with `y`;
- `max.p`, `max.q`: upper bounds for the GARCH (`p`) and ARCH (`q`) orders;
- `search_o`: subset of \(\{0,1\}\) indicating whether symmetric (`o = 0`)
  and/or asymmetric (`o = 1`) specifications are considered;
- `final_refit`: logical flag controlling whether a second “backcast refit”
  step is applied to the selected model;
- `clamp_factor`: two–element numeric vector controlling the range used to
  clamp the unconditional variance relative to the sample variance;
- `vcov.type`: type of standard errors requested from `garchx`
  (`"ordinary"` or `"robust"`).

### Grid search over \((q,p,o)\) by BIC

The function `auto_garchx()` performs a grid search over the order triple
\((q,p,o)\). Given user–supplied maxima `max.q`, `max.p` and the set
`search_o ⊂ {0,1}`, the function loops over
\[
q = 0,\ldots,\texttt{max.q}, \quad
p = 0,\ldots,\texttt{max.p}, \quad
o \in \texttt{search\_o},
\]
and fits a `garchx` model

### Illustrative simulation example

```{r auto-garchx-example, message=FALSE, warning=FALSE, echo=TRUE}
library(postshock)

## Simulate a GARCH(1,1) series
set.seed(123)
n      <- 2000
omega  <- 0.05
alpha  <- 0.07
beta   <- 0.90

eps    <- rnorm(n)
sigma2 <- numeric(n)
y      <- numeric(n)

sigma2[1] <- omega / (1 - alpha - beta)
y[1]      <- sqrt(sigma2[1]) * eps[1]

for (t in 2:n) {
  sigma2[t] <- omega + alpha * y[t-1]^2 + beta * sigma2[t-1]
  y[t]      <- sqrt(sigma2[t]) * eps[t]
}

## Run auto_garchx
best <- auto_garchx(
  y,
  max.p       = 3,
  max.q       = 3,
  search_o    = c(0L, 1L),
  final_refit = TRUE,
  vcov.type   = "robust",
  verbose     = FALSE
)

## Show selected orders and BIC
c(p = best$p, q = best$q, o = best$o)
best$bic
coef(best$fit)

```

## Synthetic volatility forecasting (`SynthVolForecast`)

The last component of the framework is a *synthetic volatility–forecasting* module,
implemented in the function `SynthVolForecast()`.  
The goal is to produce \(k\)-step–ahead **variance** forecasts for a target series
by combining a standard pre–shock GARCH model with donor–based post–shock
fixed effects.

For one target series and \(J\) donors we observe demeaned returns
\(\{y_{i,t}\}_{t=1}^n\) and, for donors, a set of contemporaneous covariates
\(x_{i,t}\).  For each series we also observe a shock time \(T_i\) and a
post–shock window length \(L_i\), supplied via the vectors `shock_time_vec` and
`shock_length_vec`, and collected into the list `Y_series_list` (target in
position 1, donors in positions 2,…,\(J+1\)).

### Donor–level GARCH–X with post–shock indicators

For each donor \(i = 1,\dots,J\) we fit a GARCH–type model with a 0/1
post–shock indicator.  Following the parametrisation of the
`garchx` package, we consider
\[
y_{i,t} = \sigma_{i,t} \varepsilon_{i,t}, \qquad
\varepsilon_{i,t} \sim \text{i.i.d. } (0,1),
\]
with conditional variance
\[
\sigma_{i,t}^2
  = \omega_i
  + \sum_{\ell=1}^{q_i} \alpha_{i,\ell} y_{i,t-\ell}^2
  + \sum_{\ell=1}^{p_i} \beta_{i,\ell} \sigma_{i,t-\ell}^2
  + \sum_{\ell=1}^{q_i} \gamma_{i,\ell} y_{i,t-\ell}^2
      \mathbf 1\{y_{i,t-\ell} < 0\}
  + \delta_i^\top x_{i,t}
  + \eta_i D_{i,t},
\]
where \(q_i\) and \(p_i\) are the ARCH and GARCH orders, and \(D_{i,t}\) is a
post–shock indicator defined by
\[
D_{i,t} =
\begin{cases}
 0, & t \le T_i, \\
 1, & T_i < t \le T_i + L_i, \\
 0, & t > T_i + L_i .
\end{cases}
\]

In the implementation we build the design matrix for donor \(i\) by stacking
the selected donor covariates (columns chosen via `covariate_indices`) together
with `post_shock_indicator`, whose coefficient corresponds to \(\eta_i\).
The function then fits either

- a user–supplied GARCH order `garch_order = c(q,p,o)`, or  
- if `garch_order = NULL`, a data–driven specification chosen by
  `auto_garchx()` via BIC over a grid in \((q,p,o)\).

After fitting, the donor–specific post–shock effect
\(\hat\omega_i^{\ast} := \hat\eta_i\) is extracted using
`lmtest::coeftest()` if available, and stored in the vector
\[
\hat\omega^{\ast} = (\hat\omega_1^{\ast},\dots,\hat\omega_J^{\ast})^\top .
\]

### Donor weighting via DBW

To transfer information from donors to the target we form a covariate
collection
\[
X_{\text{for dbw}}
  = \bigl( X_{\text{target}}, X_1,\dots,X_J \bigr),
\]
where \(X_{\text{target}}\) is the covariate matrix for the target
(`target_covariates`) and \(X_j\) is the donor–\(j\) covariate matrix
(`covariates_series_list[[j]]`).  The function `dbw()` is then used to compute
donor weights \(w = (w_1,\dots,w_J)^\top\) by solving a regularised balancing
problem on the pre–shock covariates.  The main tuning parameters are

- `dbw_indices` : which covariate columns enter the balancing problem;  
- `penalty_lambda` and `penalty_normchoice` : regularisation weight and norm;  
- `dbw_scale` and `dbw_center` : whether to standardise covariates.

The resulting combined donor shock effect is
\[
\hat\theta = \sum_{j=1}^J w_j \hat\omega_j^{\ast},
\]
which aggregates donor–level post–shock effects according to their DBW weights.

### Target GARCH and variance adjustment

For the target series we fit a **pre–shock** GARCH model *without* exogenous
regressors.  Let \(T_0\) denote the last pre–shock time for the target.  The
function `SynthVolForecast()` restricts the target data to
\(t = 1,\dots,T_0\) and fits either a user–specified `garch_order` or a
BIC–selected specification via `auto_garchx()`.  Because no `xreg` is used for
the target, forecasting does not require a future `newxreg` matrix.

Let \(\widehat v^{\text{raw}}_{0,T_0+h}\) denote the resulting
\(k\)-step–ahead **variance** forecast at horizon \(h = 1,\dots,k\).  The
DBW–adjusted volatility forecast is defined by
\[
\widehat v^{\text{adj}}_{0,T_0+h}
  = \widehat v^{\text{raw}}_{0,T_0+h} + \hat\theta ,
\]
which adds the combined donor post–shock effect \(\hat\theta\) to the raw
GARCH variance forecast.  For comparison, the function also computes an
“arithmetic–mean” adjustment that ignores DBW and uses the simple average of
donor effects,
\[
\widehat v^{\text{arith}}_{0,T_0+h}
  = \widehat v^{\text{raw}}_{0,T_0+h}
    + \frac{1}{J} \sum_{j=1}^J \hat\omega_j^{\ast} .
\]

The outputs of `SynthVolForecast()` are collected in a list with three main
components.  The element `linear_combinations` contains the donor weight vector
\(\hat w\); `predictions` contains three forecast vectors labelled
`unadjusted`, `adjusted`, and `arithmetic_mean`; and `meta` stores additional
information such as the donor–specific \(\hat\omega_j^{\ast}\), the combined
effect \(\hat\theta\), the selected GARCH orders, and the DBW convergence status.
If a vector of realised variances `ground_truth_vec` is supplied, the function
also returns QLIKE losses for each forecast version.

### Illustrative simulation example

```{r synthvol-example, echo=TRUE, message=FALSE, warning=FALSE}
library(postshock)

set.seed(123)

## 1) Simulate one target and two donor return series ----------------------
n    <- 500
eps0 <- rnorm(n)
eps1 <- rnorm(n)
eps2 <- rnorm(n)

# simple homoskedastic DGP for illustration
y0 <- eps0                     # target
y1 <- 0.8 * eps0 + 0.2 * eps1  # donor 1, highly correlated with target
y2 <- 0.5 * eps0 + 0.5 * eps2  # donor 2, less correlated

Y_list <- list(y0, y1, y2)

## 2) Simple covariates for target and donors ------------------------------
 
X1 <- cbind(x1 = rnorm(n), x2 = rnorm(n))  # donor 1 covariates
X2 <- cbind(x1 = rnorm(n), x2 = rnorm(n))  # donor 2 covariates
Xt <- cbind(x1 = rnorm(n), x2 = rnorm(n))  # target covariates  

## 3) Shock times and window lengths ---------------------------------------
shock_time_vec   <- c(350L, 350L, 350L)
shock_length_vec <- c(20L,  20L,  20L)

## 4) Call SynthVolForecast ------------------------------------------------
out_vol <- SynthVolForecast(
  Y_series_list          = Y_list,
  covariates_series_list = list(X1, X2),
  target_covariates      = Xt,
  shock_time_vec         = shock_time_vec,
  shock_length_vec       = shock_length_vec,
  k                      = 5,
  covariate_indices      = 1:2,    
  dbw_indices            = 1:2,    
  plots                  = FALSE,
  return_fits            = FALSE
)

## 5) Show number of donors, weights, and forecasts ------------------------
out_vol$meta$n_donors
out_vol$linear_combinations
out_vol$predictions
```

# Data and Empirical Setup

## Data Sources

Our empirical analysis utilizes two processed datasets distributed with the package: a validation dataset centered on Apple Inc. (AAPL) and an empirical dataset focused on ConocoPhillips (COP), a major energy producer.

The underlying raw series were originally retrieved from publicly available sources at daily frequency beginning in January 2000. Specifically, market data were obtained from Yahoo Finance via the `quantmod` package, and inflation data (CPIAUCSL) were obtained from the Federal Reserve Economic Data (FRED).

For the **COP empirical analysis**, the panel includes:

- The daily closing price of ConocoPhillips (ticker: **COP**);
- The daily closing level of the S&P 500 index (ticker: **^GSPC**);
- The daily closing price of **WTI crude oil**;
- The daily U.S. Dollar Index (ticker: DX-Y.NYB);
- The daily 3-month U.S. Treasury bill rate (ticker: ^IRX);
- The daily closing level of the **VIX volatility index** (ticker: ^VIX).

For the **Apple validation dataset**, we include:

- The daily closing price of AAPL;
- The S&P 500 index;
- The 3-month Treasury bill rate.

All series are merged by calendar date and restricted to trading days for which all variables are jointly observed. The resulting aligned panels are distributed with the package as preprocessed datasets (`cop_oil_postshock` and `aapl_control_input`), ensuring fully offline reproducibility.

## Distributed Package Objects

The package distributes two processed input objects, `cop_oil_postshock` and `aapl_control_input`, used respectively for the COP empirical study and the Apple validation example. Each object is stored as a list containing the aligned outcome series (`Y`), aligned covariate matrices (`X`), covariate names (`covar_names`), and the local shock timing and post-shock horizon information (`shock_time_vec`, `shock_length_vec`). Full descriptions of these objects are available in the package documentation.
## Construction of the Analysis Panel

Let \( P_t \) denote the nominal closing price of the target asset (AAPL or COP) at trading day \( t \). 

We treat \( \{P_t\} \) as a univariate time series and perform \(k\)-step-ahead forecasting using time-series models (e.g., ARIMA or ARIMAX). One-day-ahead forecasting corresponds to \(k = 1\), where predictions of \(P_{t+1}\) are generated using information available up to time \(t\).

Covariates observed at time \(t\), denoted by \(X_t\), consist of macro-financial variables aligned on the same trading day. These covariates are used either in donor weighting (DBW) or as exogenous regressors in ARIMAX-type models. Temporal alignment is handled internally by the forecasting procedure, and no manual lead construction is required at the data storage stage.

To study structural breaks, we extract fixed-length shock windows around each event date. Each window consists of \(T_{\text{pre}}\) pre-shock observations and \(T_{\text{post}}\) post-shock observations. The shock day is defined as the first post-shock observation within each window.

## Localized Inflation Adjustment

To ensure comparability across historical donor episodes occurring in different macroeconomic environments (e.g., 2008 or 2014), we apply a localized inflation adjustment.

Let \( \overline{\text{CPI}}_y \) denote the annual average CPI level for calendar year \(y\). Taking 2020 as the base year, we define the adjustment factor

\[
\text{adj}_y = \frac{\overline{\text{CPI}}_{2020}}{\overline{\text{CPI}}_y}.
\]

When a shock window is extracted for year \(y\), all price and covariate variables within that window are rescaled as

\[
W_y^{\text{real}} = W_y^{\text{nom}} \times \text{adj}_y.
\]

This adjustment converts all windows into 2020-dollar units while preserving within-window dynamics. Importantly, the inflation scaling is applied locally at the window level rather than globally across the full sample. This ensures that donor shock magnitudes are comparable in real terms to the 2020 target episode.

The inflation-adjusted windows are stored in the distributed datasets and serve as the inputs to the synthetic forecasting procedure.

```{r}
data("cop_oil_postshock")
data("aapl_control_input")
?cop_oil_postshock

#?aapl_control_input
```

# Simulation study

In this section we provide a targeted simulation study to illustrate how the proposed postshock forecasting framework behaves in controlled settings. The purpose of these simulations is not to deliver a comprehensive benchmark over all possible designs, but rather to verify that the adjustment mechanisms behave as expected under stylized postshock data-generating processes. We consider one set of simulations for the postshock mean equation and one for the postshock volatility equation.

All simulations were implemented in R. The R Markdown files `sim-test.Rmd` (mean equation) and `sim_vol_test.Rmd` (volatility equation) are stored in the `technical_report` folder and reproduce the examples, figures, and summary tables reported in this section.

## Targeted simulation for the postshock mean equation

### Design

For the mean equation, we use a stylized postshock simulation setup designed to mirror the empirical forecasting problem while remaining simple and interpretable. In each simulation, we generate one target series and two donor series over 200 time points, with a known shock occurring at time index 150. We focus on one-step-ahead postshock forecasting.

The donor series are constructed to differ in their similarity to the target. One donor is generated by adding only small Gaussian noise to the target path and is therefore closely aligned with the target in the pre-shock period. The second donor is generated with substantially larger noise and is intentionally less aligned. This allows us to assess whether the weighting mechanism places greater emphasis on the more informative donor.

The mean simulations implemented in `sim-test.Rmd` consider two complementary design blocks. In the first block, we study covariate informativeness by constructing one informative covariate together with additional noisy covariates. The informative covariate is generated from a common latent signal with small perturbations, whereas the noisy covariates are generated independently as random-walk-type processes. This design is used to examine how forecast performance changes as the covariate set becomes less informative.

In the second block, we study several representative postshock patterns: a one-period local jump, a persistent level shift, and a volatility-type disturbance added after the shock date. These scenarios are designed to check whether the proposed adjustment procedure responds in the expected direction under simple but interpretable departures from the pre-shock trajectory.

Throughout, the shock date and local window structure are treated as known.

### Forecasting procedures and evaluation criteria

For each simulated design, we construct the target and donor series together with their aligned covariates and pass them to `SynthPrediction()` using the same basic workflow as in the empirical application. We focus on one-step-ahead postshock prediction (\(k = 1\)).

We compare three forecasts for the target series:

1. **Unadjusted forecast.**  
   The baseline ARIMA/ARIMAX model is fitted using only the pre-shock segment of the target series, and the one-step-ahead postshock prediction is obtained without any donor-based shock adjustment.

2. **Arithmetic-mean adjusted forecast.**  
   The baseline prediction is augmented by the simple average of the estimated donor shock effects.

3. **DBW-adjusted forecast.**  
   The baseline prediction is augmented by a donor-balancing-weights (DBW) combination of the estimated donor shock effects, where the donor weights are chosen to better match the target’s pre-shock covariate environment.

Performance is assessed by comparing the predicted postshock value with the realized postshock value of the target series. In the covariate-sensitivity experiments, we summarize forecast errors and predicted-versus-realized values across alternative covariate designs. In the shock-pattern experiments, we compare the direction and magnitude of the forecast adjustments under different stylized postshock scenarios.

### Forecasting procedures and evaluation criteria

For each simulated design, we construct the target and donor series together with their aligned covariates and pass them to `SynthPrediction()` using the same basic workflow as in the empirical application. We focus on one-step-ahead postshock prediction (\(k = 1\)).

We compare three forecasts for the target series:

1. **Unadjusted forecast.**  
   The baseline ARIMA/ARIMAX model is fitted using only the pre-shock segment of the target series, and the one-step-ahead postshock prediction is obtained without any donor-based shock adjustment.

2. **Arithmetic-mean adjusted forecast.**  
   The baseline prediction is augmented by the simple average of the estimated donor shock effects.

3. **DBW-adjusted forecast.**  
   The baseline prediction is augmented by a donor-balancing-weights (DBW) combination of the estimated donor shock effects, where the donor weights are chosen to better match the target’s pre-shock covariate environment.

Performance is assessed by comparing the predicted postshock value with the realized postshock value of the target series. In the covariate-sensitivity experiments, we summarize forecast errors and predicted-versus-realized values across alternative covariate designs. In the shock-pattern experiments, we compare the direction and magnitude of the forecast adjustments under different stylized postshock scenarios.

### Reproducibility

The complete implementation of the mean-equation simulation study is provided in `sim-test.Rmd` in the `technical_report` folder. The main text reports only the representative designs and summary results.
```{r mean_sim_round23_results, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=8, fig.height=5}
library(xts)
library(ggplot2)
library(knitr)

# =========================
# Round 2: Data generation
# =========================
set.seed(123)

dates <- seq.Date(
  from = as.Date("2021-01-01"),
  by   = "day",
  length.out = 200
)

y0_values <- cumsum(rnorm(200, mean = 0, sd = 1)) + 100
Y0 <- xts(y0_values, order.by = dates)

y1_values <- y0_values + rnorm(200, mean = 0, sd = 0.1)
Y1 <- xts(y1_values, order.by = dates)

y2_values <- y0_values + rnorm(200, mean = 0, sd = 2)
Y2 <- xts(y2_values, order.by = dates)

Y_series_list <- list(Y0, Y1, Y2)

# Construct corresponding covariate series X0, X1, X2
base_signal <- cumsum(rnorm(200, mean = 0, sd = 1))

X0_values <- base_signal + rnorm(200, mean = 0, sd = 0.1)
X1_values <- base_signal + rnorm(200, mean = 0, sd = 0.1)
X2_values <- cumsum(rnorm(200, mean = 0, sd = 2))

X0 <- xts(X0_values, order.by = dates)
X1 <- xts(X1_values, order.by = dates)
X2 <- xts(X2_values, order.by = dates)

shock_time_vec   <- c(150, 150, 150)
shock_length_vec <- c(1, 1, 1)

covariates_series_list <- list(X0, X1, X2)

# Optional sanity call, kept here to match your original workflow
res_with_cov <- SynthPrediction(
  Y_series_list          = Y_series_list,
  covariates_series_list = covariates_series_list,
  shock_time_vec         = shock_time_vec,
  shock_length_vec       = shock_length_vec,
  k                      = 1,
  covariate_indices      = 1,
  seasonal               = FALSE,
  plots                  = FALSE
)

# ==========================================
# Round 3: Covariate sensitivity experiment
# ==========================================
set.seed(123)

len   <- nrow(Y_series_list[[1]])
dates <- index(Y_series_list[[1]])

generate_covariates <- function(k) {
  base_signal <- cumsum(rnorm(len))
  mat <- sapply(seq_len(k), function(j) {
    if (j == 1) {
      base_signal + rnorm(len, 0, 0.1)
    } else {
      cumsum(rnorm(len, 0, 3))
    }
  })
  xts(mat, order.by = dates)
}

abs_error <- function(pred, truth) {
  p <- as.numeric(pred)
  t <- as.numeric(truth)
  abs(p - t)
}

results  <- list()
error_df <- data.frame()
value_df <- data.frame()

for (k in c(1, 3, 5)) {

  cov_list <- lapply(seq_along(Y_series_list), function(i) generate_covariates(k))

  res <- SynthPrediction(
    Y_series_list          = Y_series_list,
    covariates_series_list = cov_list,
    shock_time_vec         = shock_time_vec,
    shock_length_vec       = shock_length_vec,
    k                      = 1,
    covariate_indices      = 1:k,
    seasonal               = FALSE,
    plots                  = FALSE,
    penalty_lambda         = 1e-4,
    penalty_normchoice     = "l2"
  )

  true_val  <- as.numeric(Y_series_list[[1]][shock_time_vec[1] + 1])
  arima_val <- as.numeric(res$predictions$unadjusted)
  synth_val <- as.numeric(res$predictions$adjusted)
  mean_val  <- as.numeric(res$predictions$arithmetic_mean)

  err_arima <- abs_error(arima_val, true_val)
  err_synth <- abs_error(synth_val, true_val)
  err_mean  <- abs_error(mean_val,  true_val)

  results[[paste0("k_", k)]] <- list(
    error_arima    = err_arima,
    error_synth    = err_synth,
    error_mean_adj = err_mean,
    weights        = res$linear_combinations,
    true_value     = true_val,
    pred_arima     = arima_val,
    pred_synth     = synth_val,
    pred_mean      = mean_val
  )

  error_df <- rbind(
    error_df,
    data.frame(k = k, Method = "ARIMA",           Error = err_arima),
    data.frame(k = k, Method = "Arithmetic mean", Error = err_mean),
    data.frame(k = k, Method = "DBW adjusted",    Error = err_synth)
  )

  value_df <- rbind(
    value_df,
    data.frame(k = k, Method = "True value",      Value = true_val),
    data.frame(k = k, Method = "ARIMA",           Value = arima_val),
    data.frame(k = k, Method = "Arithmetic mean", Value = mean_val),
    data.frame(k = k, Method = "DBW adjusted",    Value = synth_val)
  )
}

knitr::kable(
  error_df,
  digits = 3,
  caption = "Absolute forecast error across alternative covariate designs."
)

ggplot(error_df, aes(x = factor(k), y = Error, group = Method, shape = Method)) +
  geom_line() +
  geom_point(size = 3) +
  labs(
    title = "Forecast error under different numbers of covariates",
    x = "Number of covariates",
    y = "Absolute error"
  ) +
  theme_minimal()

knitr::kable(
  value_df,
  digits = 3,
  caption = "True and predicted postshock values across covariate designs."
)

ggplot(value_df, aes(x = factor(k), y = Value, group = Method, shape = Method)) +
  geom_line() +
  geom_point(size = 3) +
  labs(
    title = "Predicted versus true postshock values",
    x = "Number of covariates",
    y = "Postshock value"
  ) +
  theme_minimal()
```


## Simulation for the volatility equation

### Estimators and evaluation criteria

For each simulated data set, we first use `auto_garchx()` to select a GARCHX-type specification for each series by BIC, allowing for both symmetric and asymmetric (GJR-type) variance dynamics. The selected model may then be refitted using the backcast-based stabilization step implemented in `auto_garchx()`. Based on these fitted pre-shock volatility models, we apply `SynthVolForecast()` to construct postshock variance forecasts for the target series.

In the volatility simulations reported here, we compare two forecasts for the target variance:

1. **Unadjusted volatility forecast.**  
   A pre-shock GARCHX-type model selected by `auto_garchx()` is fitted to the target series, and its postshock conditional variance forecast is extrapolated without donor-based correction.

2. **DBW-adjusted volatility forecast.**  
   The unadjusted variance forecast is augmented by a donor-based postshock adjustment, where donor shock effects are combined using donor balancing weights constructed from pre-shock volatility features.

Performance is evaluated by comparing the predicted conditional variance with the true conditional variance generated by the simulation design. In the representative omega-jump design, we report step-by-step true variance, raw forecast, adjusted forecast, and their corresponding absolute forecast errors over the short postshock horizon.

### Estimators and evaluation criteria

For each simulated data set, we first use `auto_garchx()` to select a GARCHX-type specification for each series by BIC, allowing for both symmetric and asymmetric (GJR-type) variance dynamics. The selected model may then be refitted using the backcast-based stabilization step implemented in `auto_garchx()`. Based on these fitted pre-shock volatility models, we apply `SynthVolForecast()` to construct postshock variance forecasts for the target series.

In the volatility simulations reported here, we compare two forecasts for the target variance:

1. **Unadjusted volatility forecast.**  
   A pre-shock GARCHX-type model selected by `auto_garchx()` is fitted to the target series, and its postshock conditional variance forecast is extrapolated without donor-based correction.

2. **DBW-adjusted volatility forecast.**  
   The unadjusted variance forecast is augmented by a donor-based postshock adjustment, where donor shock effects are combined using donor balancing weights constructed from pre-shock volatility features.

Performance is evaluated by comparing the predicted conditional variance with the true conditional variance generated by the simulation design. In the representative omega-jump design, we report step-by-step true variance, raw forecast, adjusted forecast, and the corresponding absolute forecast errors over the short postshock horizon.

### Results

The representative volatility simulation under the omega-jump design shows that the unadjusted pre-shock GARCH-type forecast tends to underreact to the increase in conditional variance after the shock. In contrast, the DBW-adjusted forecast moves closer to the true postshock variance over the short forecast horizon.

Table X reports the step-by-step true conditional variance together with the raw and DBW-adjusted forecasts. In the representative design considered here, the adjusted forecast yields smaller absolute forecast errors than the unadjusted forecast at each postshock horizon. Figure X visualizes the same comparison and shows that the DBW-adjusted path tracks the true variance more closely than the raw baseline forecast.

These results are consistent with the intended role of the synthetic volatility module: when donor episodes are weighted according to pre-shock similarity in volatility features, donor information can improve short-horizon postshock variance forecasting relative to a purely pre-shock GARCH-type extrapolation.

```{r volatility_sim_results, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
library(garchx)
library(zoo)
library(ggplot2)
library(knitr)

# ====== 1) Simulation: GJR-GARCH(1,1) with an omega jump ======
sim_gjr_omega_jump <- function(n, t0,
                               omega = 0.02, d_omega = 0.06,
                               alpha = 0.07, beta = 0.80, gamma = 0.25,
                               seed = NULL) {
  if (!is.null(seed)) set.seed(seed)
  stopifnot(alpha + beta + 0.5 * gamma < 1)

  z <- rnorm(n)
  h <- e <- numeric(n)

  h[1] <- omega / (1 - alpha - beta - 0.5 * gamma)
  e[1] <- sqrt(h[1]) * z[1]

  for (t in 2:n) {
    omega_t <- if (t > t0) omega + d_omega else omega
    Ineg <- as.numeric(e[t - 1] < 0)

    h[t] <- omega_t +
      alpha * e[t - 1]^2 +
      gamma * Ineg * e[t - 1]^2 +
      beta  * h[t - 1]

    e[t] <- sqrt(h[t]) * z[t]
  }

  list(y = e, h = h)
}

# ====== 2) DBW feature construction ======
make_dbw_features <- function(y, L = 10) {
  v2 <- y^2

  msq5  <- rollapplyr(v2,  5, mean, partial = TRUE)
  msq10 <- rollapplyr(v2, 10, mean, partial = TRUE)
  msq20 <- rollapplyr(v2, 20, mean, partial = TRUE)
  vol10 <- rollapplyr(y, 10, sd, partial = TRUE)

  lag_one <- function(x, k) {
    if (k == 0) x else c(rep(x[1], k), x[1:(length(x) - k)])
  }

  lag_block <- sapply(0:(L - 1), function(k) lag_one(v2, k))
  colnames(lag_block) <- paste0("v2_lag", 0:(L - 1))

  as.data.frame(cbind(msq5, msq10, msq20, vol10, lag_block))
}

# ====== 3) Generate target + donors ======
set.seed(2025)
n  <- 1600
t0 <- 1200

tar <- sim_gjr_omega_jump(n, t0, d_omega = 0.06)
d1  <- sim_gjr_omega_jump(n, t0, d_omega = 0.08)
d2  <- sim_gjr_omega_jump(n, t0, d_omega = 0.04)
d3  <- sim_gjr_omega_jump(n, t0, d_omega = 0.02)

Y_series_list <- list(tar$y, d1$y, d2$y, d3$y)

target_covariates      <- make_dbw_features(tar$y, L = 10)
covariates_series_list <- lapply(Y_series_list[-1], make_dbw_features, L = 10)

shock_time_vec   <- rep(as.integer(t0), length(Y_series_list))
shock_length_vec <- vapply(
  Y_series_list,
  function(y) pmax(1L, as.integer(length(y) - as.integer(t0))),
  integer(1L)
)

# ====== 4) Run SynthVolForecast over a short postshock horizon ======
k <- 2

res <- SynthVolForecast(
  Y_series_list          = Y_series_list,
  covariates_series_list = covariates_series_list,
  target_covariates      = target_covariates,
  shock_time_vec         = shock_time_vec,
  shock_length_vec       = shock_length_vec,
  k                      = k,
  dbw_indices            = 1:ncol(target_covariates),
  covariate_indices      = NULL,
  max.p = 3, max.q = 3,
  plots = FALSE
)

true_var <- tar$h[(t0 + 1):(t0 + k)]
pred_raw <- as.numeric(res$predictions$unadjusted)
pred_adj <- as.numeric(res$predictions$adjusted)

vol_df <- data.frame(
  Step = seq_len(k),
  `True variance` = round(true_var, 6),
  `Raw forecast` = round(pred_raw, 6),
  `DBW-adjusted forecast` = round(pred_adj, 6),
  `Raw absolute error` = round(abs(pred_raw - true_var), 6),
  `Adjusted absolute error` = round(abs(pred_adj - true_var), 6)
)

knitr::kable(
  vol_df,
  digits = 6,
  caption = "Volatility simulation summary for the omega-jump design."
)

plot_df <- rbind(
  data.frame(Step = seq_len(k), Series = "True variance", Value = true_var),
  data.frame(Step = seq_len(k), Series = "Raw forecast", Value = pred_raw),
  data.frame(Step = seq_len(k), Series = "DBW-adjusted forecast", Value = pred_adj)
)

ggplot(plot_df, aes(x = Step, y = Value, group = Series, shape = Series)) +
  geom_line() +
  geom_point(size = 3) +
  labs(
    title = "True versus predicted variance under the omega-jump design",
    x = "Horizon step",
    y = "Variance"
  ) +
  theme_minimal()
```

## Discussion

The simulation studies for the postshock mean and volatility components provide controlled settings in which the underlying shock effects and conditional moments are known. In these settings, the unadjusted baseline forecasts tend to underreact to structural changes because they are estimated using only pre-shock information and therefore extrapolate the pre-shock dynamics too smoothly into the postshock period.

For the mean component, incorporating donor information can improve postshock prediction, but the quality of the adjustment depends on how well the donor episodes resemble the target in the pre-shock period. The targeted simulations show that simple unweighted adjustments can become less stable when donor series or covariates are noisy, whereas the DBW-based adjustment remains more robust by placing greater emphasis on donors that are better aligned with the target.

For the volatility component, the representative omega-jump designs show a similar pattern. The unadjusted pre-shock GARCH-type variance forecast tends to underpredict the postshock increase in conditional variance, while the DBW-adjusted forecast tracks the true postshock variance more closely over the short forecast horizon. This supports the use of pre-shock volatility features for donor weighting in the synthetic volatility module.

Taken together, these simulation results support the role of donor balancing weights as a general device for improving postshock forecasting in both the mean and volatility settings. They also provide a controlled complement to the empirical analysis in the next section, where the same workflow is applied to the ConocoPhillips case study.


# Empirical Application: ConocoPhillips under Large Shocks

In this section we apply the postshock forecasting framework developed in Sections 2–3 to the ConocoPhillips (COP) data set described in Section 4. The goal is to forecast COP around large negative shocks by borrowing information from earlier donor shock episodes that occurred under different market conditions. We treat the COVID-19 oil price collapse in March 2020 as the target episode and use several earlier crisis episodes as donors.

## Target and donor shock episodes

We focus on the large negative shock to ConocoPhillips on 9 March 2020 as the target episode. In the implementation we follow the convention of Section 3 and treat the last pre-shock trading day as the index \(T_0\). For the March 2020 event this corresponds to 6 March 2020, so the shock itself occurs between \(T_0\) and \(T_0 + 1\).

As donor episodes we select five earlier crisis windows for COP. These correspond to the March 2008 Bear Stearns episode, three major September 2008 crisis episodes during the Lehman and bailout turmoil, and the late-November 2014 OPEC-related oil price collapse. For each episode we construct a local window of 30 trading days before \(T_0\) and 30 trading days after the shock, and we work with inflation-adjusted prices expressed in 2020 U.S. dollars, as described in Section 4.
## Empirical implementation using the packaged data object

To keep the empirical workflow fully reproducible and consistent with the package interface, we use the processed object `cop_oil_postshock` distributed with the package rather than reconstructing the windows manually in the main text. This object contains the aligned target and donor shock windows, the corresponding macro-financial covariate matrices, and the shock timing metadata required by the forecasting functions.

In particular, `cop_oil_postshock` stores the outcome series in `Y`, the aligned covariate matrices in `X`, the covariate names in `covar_names`, and the local shock timing information in `shock_time_vec` and `shock_length_vec`. The empirical analysis therefore follows the same workflow as the general package implementation and can be reproduced directly from the processed object.

Using the same processed object, we next examine whether separating donor episodes into multiple pools provides a more interpretable or more accurate postshock adjustment for the March 2020 COP episode.

```{r cop-empirical-call, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
library(ggplot2)
library(knitr)
data("cop_oil_postshock")

out_cop <- SynthPrediction(
  Y_series_list          = cop_oil_postshock$Y,
  covariates_series_list = cop_oil_postshock$X,
  shock_time_vec         = cop_oil_postshock$shock_time_vec,
  shock_length_vec       = cop_oil_postshock$shock_length_vec,
  k                      = 1,
  covariate_indices      = NULL,
  seasonal               = TRUE,
  use_dbw                = TRUE,
  plots                  = FALSE
)

forecast_df <- data.frame(
  Method = c("Actual", "Unadjusted", "Arithmetic mean", "DBW adjusted"),
  Value  = c(
    as.numeric(cop_oil_postshock$Y[[1]][cop_oil_postshock$shock_time_vec[1] + 1]),
    as.numeric(out_cop$predictions$unadjusted),
    as.numeric(out_cop$predictions$arithmetic_mean),
    as.numeric(out_cop$predictions$adjusted)
  )
)

knitr::kable(
  forecast_df,
  digits = 3,
  caption = "Forecast comparison for the March 2020 COP shock episode."
)

weight_df <- data.frame(
  Donor = names(cop_oil_postshock$Y)[-1],
  Weight = as.numeric(out_cop$linear_combinations)
)

knitr::kable(
  weight_df,
  digits = 3,
  caption = "DBW donor weights for the COP empirical application."
)

target_y <- as.numeric(cop_oil_postshock$Y[[1]])
shock_t0 <- cop_oil_postshock$shock_time_vec[1]
pred_day <- shock_t0 + 1

plot_df <- data.frame(
  Day = 1:pred_day,
  COP = target_y[1:pred_day]
)

forecast_points <- data.frame(
  Day = c(pred_day, pred_day - 0.15, pred_day + 0.15, pred_day + 0.30),
  Method = factor(
    c("Actual", "Unadjusted", "Arithmetic mean", "DBW adjusted"),
    levels = c("Actual", "Unadjusted", "Arithmetic mean", "DBW adjusted")
  ),
  Value = c(
    as.numeric(target_y[pred_day]),
    as.numeric(out_cop$predictions$unadjusted),
    as.numeric(out_cop$predictions$arithmetic_mean),
    as.numeric(out_cop$predictions$adjusted)
  )
)

ggplot() +
  geom_line(data = plot_df, aes(x = Day, y = COP), color = "black") +
  geom_point(data = plot_df, aes(x = Day, y = COP), color = "black") +
  geom_vline(xintercept = pred_day, linetype = "dashed") +
  geom_point(
    data = forecast_points,
    aes(x = Day, y = Value, color = Method, shape = Method),
    size = 3
  ) +
  scale_color_manual(values = c(
    "Actual" = "black",
    "Unadjusted" = "red",
    "Arithmetic mean" = "blue",
    "DBW adjusted" = "darkgreen"
  )) +
  labs(
    title = "COP path up to the forecast date with postshock forecast comparison",
    x = "Day in local shock window",
    y = "COP price"
  ) +
  theme_minimal()
```

## MultiPool extension

### Motivation

The single-pool donor adjustment treats all historical donor episodes as belonging to a common donor set. In the COP application, however, this may be restrictive because the March 2020 collapse plausibly reflected multiple channels, including oil-market supply disruptions and broader demand or financial-stress effects. A MultiPool extension allows these channels to be represented separately by grouping donor episodes into economically interpretable pools and aggregating their contributions afterwards.

### Pool definition

Using the same COP shock windows as in the baseline empirical analysis, we partition the donor episodes into two pools. The late-November 2014 episode is assigned to a **supply** pool because it is naturally associated with the OPEC-related oil-price collapse. The March and September 2008 episodes are assigned to a **demand** pool, as they are more closely associated with crisis-driven market stress and demand contraction.

Formally, the pool structure is specified as
\[
\texttt{pools} =
\{\texttt{supply} = (\texttt{Y\_2014\_11\_28}),\;
\texttt{demand} = (\texttt{Y\_2008\_03\_17}, \texttt{Y\_2008\_09\_09}, \texttt{Y\_2008\_09\_15}, \texttt{Y\_2008\_09\_29})\}.
\]

### MultiPool implementation

We apply the MultiPool version of `SynthPrediction()` using the same aligned COP outcome and covariate series as in the baseline case. In this experiment, donor balancing weights are applied within each pool (`pool_use_dbw = TRUE`), while the baseline target forecast is kept as the unweighted ARIMA/ARIMAX component (`base_use_dbw = FALSE`).

We consider two aggregation rules across pools:

1. **Sum aggregation** (`pool_agg = "sum"`), which adds the estimated pool-level shock effects;
2. **Weighted aggregation** (`pool_agg = "weighted"`), which combines the pool-level shock effects using user-specified pool weights.

This comparison allows us to assess whether separating supply-side and demand-side donor pools yields a more interpretable or more accurate postshock adjustment than the single-pool specification.
```{r cop-multipool-call, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
library(knitr)

pre_len  <- 30L
post_len <- 1L
k <- 1L

Y_series_list          <- cop_oil_postshock$Y
covariates_series_list <- cop_oil_postshock$X

shock_time_vec   <- rep(pre_len,  length(Y_series_list))
shock_length_vec <- rep(post_len, length(Y_series_list))

pools <- list(
  supply = c("Y_2014_11_28"),
  demand = c("Y_2008_03_17", "Y_2008_09_09", "Y_2008_09_15", "Y_2008_09_29")
)

# MultiPool with additive aggregation
out_sum <- SynthPrediction(
  Y_series_list          = Y_series_list,
  covariates_series_list = covariates_series_list,
  shock_time_vec         = shock_time_vec,
  shock_length_vec       = shock_length_vec,
  k                      = k,
  pools                  = pools,
  pool_agg               = "sum",
  base_use_dbw           = FALSE,
  pool_use_dbw           = TRUE,
  plots                  = FALSE
)

# MultiPool with weighted aggregation
out_wsum <- SynthPrediction(
  Y_series_list          = Y_series_list,
  covariates_series_list = covariates_series_list,
  shock_time_vec         = shock_time_vec,
  shock_length_vec       = shock_length_vec,
  k                      = k,
  pools                  = pools,
  pool_agg               = "weighted",
  pool_weights           = c(supply = 0.9, demand = 0.9),
  base_use_dbw           = FALSE,
  pool_use_dbw           = TRUE,
  plots                  = FALSE
)

multipool_df <- data.frame(
  Method = c("Actual", "Unadjusted", "Single-pool DBW", "MultiPool (sum)", "MultiPool (weighted)"),
  Value  = c(
    as.numeric(cop_oil_postshock$Y[[1]][pre_len + 1]),
    as.numeric(out_cop$predictions$unadjusted),
    as.numeric(out_cop$predictions$adjusted),
    as.numeric(out_sum$predictions$adjusted_multipool),
    as.numeric(out_wsum$predictions$adjusted_multipool)
  )
)

knitr::kable(
  multipool_df,
  digits = 3,
  caption = "Forecast comparison for the COP empirical application under MultiPool specifications."
)
target_y <- as.numeric(cop_oil_postshock$Y[[1]])
pred_day <- pre_len + 1L

path_df <- data.frame(
  Day = seq_len(pred_day),
  Price = target_y[seq_len(pred_day)]
)

forecast_df <- data.frame(
  Day = c(pred_day, pred_day + 0.10, pred_day + 0.20, pred_day + 0.30, pred_day + 0.40),
  Method = factor(
    c("Actual", "Unadjusted", "Single-pool DBW", "MultiPool (sum)", "MultiPool (weighted)"),
    levels = c("Actual", "Unadjusted", "Single-pool DBW", "MultiPool (sum)", "MultiPool (weighted)")
  ),
  Value = c(
    as.numeric(cop_oil_postshock$Y[[1]][pred_day]),
    as.numeric(out_cop$predictions$unadjusted),
    as.numeric(out_cop$predictions$adjusted),
    as.numeric(out_sum$predictions$adjusted_multipool),
    as.numeric(out_wsum$predictions$adjusted_multipool)
  )
)

ggplot() +
  geom_line(
    data = path_df,
    aes(x = Day, y = Price),
    color = "grey55",
    linewidth = 0.8
  ) +
  geom_point(
    data = path_df,
    aes(x = Day, y = Price),
    color = "black",
    size = 2
  ) +
  geom_point(
    data = forecast_df,
    aes(x = Day, y = Value, color = Method, shape = Method),
    size = 3.2
  ) +
  scale_color_manual(values = c(
    "Actual" = "black",
    "Unadjusted" = "#F4A3A3",
    "Single-pool DBW" = "#8DB6F2",
    "MultiPool (sum)" = "#9ED9A3",
    "MultiPool (weighted)" = "#C8A2E8"
  )) +
  scale_shape_manual(values = c(
    "Actual" = 16,
    "Unadjusted" = 17,
    "Single-pool DBW" = 15,
    "MultiPool (sum)" = 18,
    "MultiPool (weighted)" = 3
  )) +
  labs(
    title = "COP path up to the forecast date under single-pool and MultiPool specifications",
    x = "Day in local shock window",
    y = "COP price"
  ) +
  theme_minimal()
```

## Summary and discussion

In this empirical section we applied the postshock forecasting framework to the ConocoPhillips data set using the processed package object `cop_oil_postshock`. The COVID-19 oil-price collapse of 9 March 2020 was treated as the target episode, while five earlier crisis windows from 2008 and 2014 served as donor episodes. The packaged object contains the aligned target and donor outcome series, the corresponding macro-financial covariate matrices, and the associated shock metadata, allowing the empirical workflow to be reproduced directly through the package interface.

The baseline empirical results illustrate the contribution of donor information relative to the unadjusted ARIMAX forecast. The unadjusted forecast, obtained by extrapolating the pre-shock target dynamics without any donor-based correction, lies substantially above the realised COP price on the shock date. Both the arithmetic-mean adjustment and the DBW-adjusted forecast move closer to the realised value, with the DBW-adjusted version performing slightly better in this case. This supports the idea that reweighting donor episodes according to pre-shock similarity can improve postshock prediction relative to simple averaging.

The MultiPool extension further enriches the empirical analysis by allowing donor episodes to be partitioned into economically interpretable groups. In the COP application, the donor episodes were separated into supply-related and demand-related pools, reflecting the view that the March 2020 collapse likely combined multiple transmission channels. The MultiPool results show that this extension can provide a more structured and interpretable decomposition of the postshock adjustment, while also yielding forecasts that are competitive with, and in this case slightly closer to the realised value than, the single-pool DBW forecast.

Overall, the COP case study demonstrates that the proposed framework can transfer information from historical shock episodes to a new target event in a reproducible and modular way. The same package workflow can be adapted to alternative donor structures, additional pooling rules, or other financial and macroeconomic time series, making the framework flexible for a broad class of postshock forecasting problems.


# Empirical Extension: Apple in the Presence of Control Shocks

In this section we consider an Apple (AAPL) example designed to illustrate the control-shock extension of the postshock forecasting framework. Unlike the ConocoPhillips case, where the main focus was on transferring information across donor shock episodes and on decomposing donor structure through the MultiPool specification, the Apple example is intended to show how the framework can be adapted when the postshock movement of interest may be confounded by additional market-wide or background shocks.

## Motivation and empirical setting

Apple provides a useful case study because product-release events often generate stock-price movements that are plausibly mixed with broader market conditions. In such settings, the observed postshock movement in the target series may reflect both the event-specific shock of interest and an additional control component that is not unique to the target event. This motivates a control-shock formulation, in which the forecasting procedure seeks to separate the event-specific adjustment from more general background movements.

Following the validation design used in the Apple study, we treat one Apple shock window as the target episode and use several earlier Apple-related windows as donor episodes. The donor windows are selected to capture similar event environments while still allowing heterogeneity in the realised postshock responses. As in the COP application, all windows are locally aligned and inflation-adjusted, and the analysis is carried out on trading-day windows centered around the event date.

## Empirical implementation using the packaged data object

To keep the Apple validation study reproducible and aligned with the package interface, we use the processed object `aapl_control_input` distributed with the package. This object contains the aligned target and donor outcome series, the corresponding macro-financial covariate matrices, and the associated local shock timing information required by the synthetic forecasting procedure.

In particular, `aapl_control_input` stores the outcome series in `Y`, the aligned covariate matrices in `X`, the covariate names in `covar_names`, and the local shock metadata in `shock_time_vec` and `shock_length_vec`. Thus, the Apple analysis can be implemented directly from the packaged object without reconstructing the event windows manually in the main text.

In the control-shock experiment, we supplement these packaged inputs with an explicit control-shock specification within the target window and then pass all components to `SynthPrediction()`. The adjusted forecast reported below is therefore obtained under the control-shock setup, while the unadjusted forecast is the corresponding benchmark based only on the pre-shock target dynamics.

```{r aapl-controlshock-call, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
library(knitr)
library(ggplot2)

data("aapl_control_input")

Y_series_list          <- aapl_control_input$Y
covariates_series_list <- aapl_control_input$X
shock_time_vec         <- aapl_control_input$shock_time_vec
shock_length_vec       <- aapl_control_input$shock_length_vec

# control shock specification for the target window
# replace this with the exact local index you want to use
control_shocks <- list(
  list(time = 10L, length = 1L, shape = "point")
)

out_aapl <- SynthPrediction(
  Y_series_list            = Y_series_list,
  covariates_series_list   = covariates_series_list,
  shock_time_vec           = shock_time_vec,
  shock_length_vec         = shock_length_vec,
  k                        = 1,
  use_dbw                  = TRUE,
  dbw_indices              = 1:2,
  covariate_indices        = NULL,
  seasonal                 = FALSE,
  control_shocks           = control_shocks,
  dbw_center               = TRUE,
  dbw_scale                = TRUE,
  days_before_shocktime_vec = 10L,
  plots                    = FALSE
)

actual_aapl <- as.numeric(
  Y_series_list[[1]][shock_time_vec[1] + 1]
)

aapl_result_df <- data.frame(
  Method = c("Actual", "Unadjusted", "Adjusted"),
  Value  = c(
    actual_aapl,
    as.numeric(out_aapl$predictions$unadjusted),
    as.numeric(out_aapl$predictions$adjusted)
  )
)

knitr::kable(
  aapl_result_df,
  digits = 3,
  caption = "Forecast comparison for the Apple control-shock experiment."
)

aapl_donor_names <- c("2017-06-06", "2018-10-30", "2019-06-03")
aapl_weights <- as.numeric(out_aapl$meta$weights)

aapl_weight_df <- data.frame(
  Donor  = aapl_donor_names[seq_along(aapl_weights)],
  Weight = aapl_weights
)

knitr::kable(
  aapl_weight_df,
  digits = 3,
  caption = "DBW donor weights for the Apple control-shock experiment."
)
```

 
```{r aapl-plot-data, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
# target path
aapl_target_y <- as.numeric(Y_series_list[[1]])
aapl_n <- length(aapl_target_y)

# actual value at the forecast horizon
actual_aapl <- as.numeric(
  Y_series_list[[1]][shock_time_vec[1] + 1]
)

# predictions
aapl_unadjusted <- as.numeric(out_aapl$predictions$unadjusted)
aapl_adjusted   <- as.numeric(out_aapl$predictions$adjusted)

# main path data
aapl_path_df <- data.frame(
  Day = seq_len(aapl_n),
  Price = aapl_target_y
)

# forecast points at the horizon
aapl_forecast_df <- data.frame(
  Day = c(
    shock_time_vec[1] + 1,
    shock_time_vec[1] + 1.10,
    shock_time_vec[1] + 1.20
  ),
  Method = factor(
    c("True value", "Unadjusted", "Adjusted"),
    levels = c("True value", "Unadjusted", "Adjusted")
  ),
  Value = c(
    actual_aapl,
    aapl_unadjusted,
    aapl_adjusted
  )
)

ggplot() +
  geom_line(
    data = aapl_path_df,
    aes(x = Day, y = Price),
    color = "#e78ac3",
    linewidth = 0.8
  ) +
  geom_point(
    data = aapl_path_df,
    aes(x = Day, y = Price),
    color = "black",
    size = 1.8
  ) +
  geom_point(
    data = aapl_forecast_df,
    aes(x = Day, y = Value, color = Method, shape = Method),
    size = 3
  ) +
  scale_color_manual(values = c(
    "True value" = "black",
    "Unadjusted" = "#e78ac3",
    "Adjusted" = "#1f78b4"
  )) +
  scale_shape_manual(values = c(
    "True value" = 16,
    "Unadjusted" = 16,
    "Adjusted" = 3
  )) +
  labs(
    title = "Apple target window with postshock forecast comparison",
    x = "Day",
    y = "Closing stock price"
  ) +
  theme_minimal()
```
## Results

The Apple example is used to illustrate the control-shock version of the forecasting framework. Using the processed object `aapl_control_input`, we construct the target and donor windows, specify the local shock timing information, and then estimate the postshock forecast under a control-shock specification.

In this implementation, the reported adjusted forecast already incorporates the control-shock structure through the `control_shocks` argument in `SynthPrediction()`. Accordingly, the empirical comparison focuses on three quantities: the realised postshock value, the unadjusted forecast based only on pre-shock target dynamics, and the adjusted forecast obtained after incorporating donor-based information under the control-shock setup.

In this example, the realised postshock Apple price is 119.490, compared with an unadjusted forecast of 116.108 and an adjusted forecast of 117.193. Thus, the adjusted forecast moves closer to the realised value than the unadjusted forecast, although some underprediction remains. This indicates that the framework remains useful in settings where the observed postshock movement is interpreted in the presence of an additional control component, rather than as a purely isolated target shock.



# Conclusion

This technical report developed a modular postshock forecasting framework for time series with structural breaks in both mean and volatility. The framework combines donor-based adjustment, synthetic weighting, and flexible extensions for more complex empirical settings.

The simulation studies show that donor-based adjustment improves postshock forecasting relative to unadjusted benchmarks, and that the DBW mechanism is especially useful when donor episodes differ in their pre-shock covariate environments. In the volatility setting, the framework also extends naturally to postshock variance prediction through GARCHX-type modeling.

The empirical case studies highlight two complementary forms of flexibility. In the ConocoPhillips application, the framework improves upon the unadjusted benchmark and can be further enriched through the MultiPool extension, which groups donor episodes into economically interpretable channels. In the Apple example, the control-shock formulation shows that the same forecasting core can also be applied when the observed postshock response is interpreted in the presence of an additional background component.

Taken together, these results show that the package is not limited to a single fixed application template. Instead, it supports a reproducible and modular workflow that can be adapted to alternative donor structures, different economic mechanisms, and richer interpretations of postshock behavior. Possible future work includes broader real-data volatility applications, additional pooling schemes, and further extensions of the control-shock framework.


# References

Lin, Jilei, and Daniel J. Eck (2021). “Minimizing post-shock forecasting error through
aggregation of outside information.” *International Journal of Forecasting*,
37(4), 1710–1727. https://doi.org/10.1016/j.ijforecast.2021.03.010

Sucarrat, Genaro (2021). “garchx: Flexible and Robust GARCH-X Modelling.”
*The R Journal*, 13(1), 276–291.
